Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

\subsubsection{AST Transformation}
%\todo{Big todo --> Find literature, introduce proper reasoning why I need to do this.}
CR uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code. To refactor clones, CR creates a new method declaration and moves all statements from a clone instance in the clone class to the new method. This method is placed according to the relation between the clone instances (see Sec.~\ref{sec:relation}). CR analyzes the source code of the extracted method and populates it with the following properties:
\begin{itemize}
  \item \textbf{Parameters}: For each variable used that is not accessible from the scope of the extracted method.
  \item \textbf{A return value}: If the method modifies or declares local data that is needed outside of its scope, or if the cloned fragments already returned data.
  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \\ \texttt{RuntimeException}.
\end{itemize}
CR then removes all cloned code and replaces it with a call to the newly created method. In case of a return value, CR either assigns the call result, declares it or returns it accordingly.

\subsection{Maintainability Metrics}
After applying the refactorings, CR measures the impact of the refactoring on maintainability metrics. We first state the metrics that we measure and then define the characteristics of the applied refactoring that influence the metrics.

@@

\subsection{Tool Evaluation}
We assess the correctness of CR through unit tests and empirical validation. First, we create a set of 57 control projects to verify the correctness in many (edge) cases. These projects contain clones for each relation, location, and refactorability category. 
%to see whether they get correctly identified. 
Next, we run the tool over the corpus and manually verify samples of the acquired results. We verified at least 5 clones of each relation, location and refactoring. This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.

@@

\subsubsection{Clone Token Volume} \label{sec:clonetokenvolume}
Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. For higher token volume numbers we have fewer refactorings that refactor such clones, therefore we represent the x-axis as a logarithmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

@@

\subsubsection{Return Value}
Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system. The return categories are ordered by their scores. %\todo{this sentence about relation impact seems more suitable for discussion}
Scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability. When the result of the call to the extracted method is directly returned, the maintainability score is the highest. When no value is returned, the maintainability score is the lowest. %\todo{this sentence about relation impact seems more suitable for discussion}
The main reason that "Void" is lowest, is that it is linked to a higher number of parameters required for the extracted method.

@@

\subsection{Clone Context}
Regarding clone context, our results indicate that most clones (37\%) are in a common class. This is favorable for automatic refactoring because the extracted method does not have to be moved after extraction. 24\% of clones are in a common hierarchy. These refactorings are also often favorable. Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring. 15\% of clones are in an interface. %\todo{which ...}.

@@

\subsection{Extract Method}
28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies). About 25\% of clones do not span part of a method, therefore they cannot be refactored. Many clones (23\%) do not have a statement as top-level AST-Node. Upon manual inspection, we noticed that the main reason is clones in lambda functions or in anonymous classes. About 15\% of clones span only part of an AST-Node.% \todo{and?}.

>>>>

\subsubsection{AST transformation}
%\todo{Big todo --> Find literature, introduce proper reasoning why I need to do this.}
CR uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code. To refactor clones, CR creates a new method declaration and moves all statements from a clone instance in the clone class to the new method. This method is placed according to the relation between the clone instances (see Sec.~\ref{sec:relation}). CR analyzes the source code of the extracted method and populates it with the following properties:
\begin{itemize}
  \item \textbf{Parameters}: For each variable used that is not accessible from the scope of the extracted method.
  \item \textbf{A return value}: If the method modifies or declares local data that is needed outside of its scope, or if the cloned fragments already returned data.
  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \\ \texttt{RuntimeException}.
\end{itemize}
CR then removes all cloned code and replaces it with a call to the newly created method. In case of a return value, CR either assigns the call result, declares it or returns it accordingly.

\subsection{Maintainability metrics}
After applying the refactorings, CR measures the impact of the refactoring on maintainability metrics. We first state the metrics that we measure and then define the characteristics of the applied refactoring that influence the metrics.

@@

\subsection{Tool evaluation}
We assess the correctness of CR through unit tests and empirical validation. First, we create a set of 57 control projects to verify the correctness in many (edge) cases. These projects contain clones for each relation, location, and refactorability category. 
%to see whether they get correctly identified. 
Next, we run the tool over the corpus and manually verify samples of the acquired results. We verified at least 5 clones of each relation, location and refactoring. This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.

@@

\subsubsection{Clone token volume} \label{sec:clonetokenvolume}
Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. For higher token volume numbers we have fewer refactorings that refactor such clones, therefore we represent the x-axis as a logarithmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

@@

\subsubsection{Return value}
Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system. The return categories are ordered by their scores. %\todo{this sentence about relation impact seems more suitable for discussion}
Scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability. When the result of the call to the extracted method is directly returned, the maintainability score is the highest. When no value is returned, the maintainability score is the lowest. %\todo{this sentence about relation impact seems more suitable for discussion}
The main reason that "Void" is lowest, is that it is linked to a higher number of parameters required for the extracted method.

@@

\subsection{Clone context}
Regarding clone context, our results indicate that most clones (37\%) are in a common class. This is favorable for automatic refactoring because the extracted method does not have to be moved after extraction. 24\% of clones are in a common hierarchy. These refactorings are also often favorable. Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring. 15\% of clones are in an interface. %\todo{which ...}.

@@

\subsection{Extract method}
28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies). About 25\% of clones do not span part of a method, therefore they cannot be refactored. Many clones (23\%) do not have a statement as top-level AST-Node. Upon manual inspection, we noticed that the main reason is clones in lambda functions or in anonymous classes. About 15\% of clones span only part of an AST-Node.% \todo{and?}.
